\begin{abstract}

%% Unlicensed wireless access is mainstream today, with its prime example, \wf carrying more than 70\% of wireless traffic. 
%% Unplanned, low-cost deployment and the absence of complex signalling protocols let \wf thrive. 
%% Yet, \wf and other unlicensed technologies have so far been successful only in short-range scenarios. 
%% Recently, the availability of TV white space frequencies have promised to extend the benefits of unlicensed networking to long-range scenarios. 
%% The main technology behind this drive is 802.11af, a \wf variant adapted for TV frequencies, but it has had limited adoption so far.


In this paper we study network architecture for unlicensed cellular networking for outdoor coverage in TV white spaces.
The main technology proposed for TV white spaces is 802.11af, a \wf variant adapted for TV frequencies.
However, 802.11af is originally designed for improved indoor propagation.
We show that long links, typical for outdoor use, exacerbate know Wi-Fi issues, such as hidden and exposed terminal, and significantly reduce its efficiency. 

Instead, we propose \cf, an alternative architecture based on LTE. 
LTE is designed for long-range coverage and throughput efficiency, but it is also designed to operate in tightly controlled and centrally managed networks. 
\cf overcomes these problems by designing an LTE-compatible spectrum database component, mandatory for TV white space networking,
and introducing an interference management component for distributed coordination.
\cf interference management is compatible with existing LTE mechanisms, requires no explicit communication between base stations, and is more efficient than CSMA for long links.

We evaluate our design through extensive real world evaluation on off-the-shelf LTE equipment and simulations. 
We show that, compared to 802.11af, it increases coverage by 40\% and reduces median flow completion times by 2.3x.






%% \wf is the mainstream wireless access technology today carrying more than 70\% of wireless traffic. 
%% Unplanned, low-cost deployment and the absence of complex signalling protocols let WiFi to thrive. 
%% Yet, WiFi falls short of providing the ubiquitous wireless access and the wide-area coverage demanded by modern cloud-based applications and services. 
%% On the contrary, cellular networks fulfil the goal of coverage at the expense of complex, expensive, and tightly controlled networks that stifle innovation. 

%% In this paper, we design \cf, an unlicensed cellular network that bridges WiFi and cellular technologies. 
%% \cf combines the cheap,unplanned deployment of WiFi with the long-range coverage and throughput efficiency of cellular networks. 
%% To achieve this, \cf is an LTE-based network operating in unlicensed spectrum in TVWS.  
%% To allow for interference management while supporting unplanned deployment, we design mechanisms for distributed coordination that require no explicit communication between LTE base stations. Through extensive simulations and real world experiments on off-the-shelf and custom-built LTE equipment, we show the feasibility of our design and the benefits of \cf compared to existing wireless technologies.
\end{abstract}
